Probing the Deuteron at Very Large Internal Momenta

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl.tex
updateed PRL submission docs

@@

%For $^{2}\mathrm{H}(e,e'p)n$, the low missing momentum data ($p_{\mathrm{r}}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).
%The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\

@@

%\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
%and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.

@@

%The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
%to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
%\onecolumngrid
%\begin{center}

@@

\includegraphics[scale=0.45]{prl_plots/PRL_plot1.pdf}
\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,

@@

%\end{center}
%\twocolumngrid

@@

%-----Mention the fofa parametrizations used in each of the calculations------

@@

\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
\caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.

@@

%-------------------------------

>>>>

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
\pdfoutput=1 
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

\begin{document}

\title{Probing the Deuteron at Very Large Internal Momenta}

\input authorlist.tex

\date{\today}

\begin{abstract}
  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  over a range of neutron recoil momenta, $p_{\mathrm{r}}$,  reaching up to $\sim1.0$ GeV/c. The data were
  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar currents (IC) are suppressed and
  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
\end{abstract}

\pacs{25.30.Fj, 25.60.Gc}
\maketitle

The deuteron is the only bound two-nucleon system and serves as an ideal framework to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
nucleons begin to overlap. The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}. As of the present time, there are only a few nuclear physics experiments for
which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum component) is via the exclusive deuteron
electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA), the virtual photon couples to
the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron). The neutron carries a recoil momentum, $p_{\mathrm{r}}$, equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.\\
\indent In addition to the PWIA picture, the ejected nucleon undergoes final state interactions (FSI) with the recoiling nucleon. Other contributing processes are
the photon coupling to the exchanged mesons in the $pn$ system, generating meson exchange currents (MEC), or the photon exciting the bound nucleon into the
resonating state (mainly $\Delta$-isobar) with subsequent $\Delta N \to NN$ rescattering, referred to as isobar currents (IC). FSI, MEC and IC can significantly alter the recoiling neutron
momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively\cite{sargsian_2015}.
The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}. Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the deuteron. IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance
electro-production threshold. Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$) (see Section 5 of Ref. \cite{sargsian_2015}) have helped quantify the contributions
from FSI, MEC and IC to the $^{2}\mathrm{H}(e,e'p)n$ cross sections and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{\circ}$. This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{\circ}$ and $\theta_{nq}\sim120^{\circ}$. Because at
$\theta_{nq}\sim120^{\circ}$ ($x_{\mathrm{Bj}}<1$) IC are not negligible, the $x_{\mathrm{Bj}}>1$ ($\theta_{nq}\sim40^{\circ}$) kinematics are the preferred choice to suppress IC as well as FSI. \\
\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ ($>1$ (GeV/c)$^{2}$) were carried out at Jefferson Lab (JLab) in Halls A \cite{PhysRevLett.107.262501} and B \cite{PhysRevLett.98.262502}. Both
experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles, peaking
at $\theta_{nq} \sim 70^{\circ}$ in agreement with GEA \cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
distributions for  a range of $Q^2$ values as well as momentum distributions. However, statistical limitations made it necessary to integrate over a wide angular range to determine momentum distributions
which are therefore dominated by  FSI, MEC and IC for $p_{\mathrm{r}}$ above $\sim 300$ MeV/c. \\
\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$)
reaching recoil momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$. For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
and $45\pm5^{\circ}$ compared to  $\theta_{nq}=75\pm5^{\circ}$. Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{\circ}$) compared to FSI
dominance at $\theta_{nq}=75^{\circ}$ \cite{PhysRevLett.107.262501}. \\
\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment \cite{PhysRevLett.107.262501} and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c, which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.\\

@@

@@

@@

@@

\includegraphics[scale=0.45]{PRL_plot1.pdf}
\caption{(Color online). The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,

@@

@@

@@

\includegraphics[scale=0.5]{PRL_plot2.pdf}
\caption{(Color online). The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.

@@

\bibliography{prl}
\end{document}

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/body.tex
updateed PRL submission docs

to define the overall normalization uncertainty ($\leq$ 8.4$\%$).\\

@@

The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 8.4$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties
to obtain the final uncertainty on the cross sections.\\

@@

\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,

@@

\caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.

>>>>

to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\

@@

The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\

@@

\caption{(Color online). The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,

@@

\caption{(Color online). The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
